GSE158422: DNA methylation in Lung squamous cell carcinoma - RNA expression and integration

### 2024-01-02 figs/GSE158422_rna_int.Rmd
download counts
fix
save RNA integration results

@@

pdf("fig5c.pdf")
heatmap.2( as.matrix(mtop) , trace="none",margins = c(6,25), col=colfunc(25), cexRow=.6, cexCol=1)
dev.off()

@@

>>>>

if (!file.exists("GSE158420_counts.txt.gz")) {
  download.file("https://www.ncbi.nlm.nih.gov/geo/download/?acc=GSE158420&format=file&file=GSE158420%5Fcounts%2Etxt%2Egz",
    destfile="GSE158420_counts.txt.gz")
}

@@

pdf("fig5c.pdf")
heatmap.2( as.matrix(mtop) , trace="none",margins = c(6,25), col=colfunc(25), cexRow=.7, cexCol=1)
dev.off()

@@

save.image("GSE158422_rna_int.Rdata")
